Performance of two different ontological and data access methods

### 2014-07-10 cold2014/magnus.tex
rewrite the DanielPlot section a bit
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@745 43ef1190-90fd-4dd7-a769-d0121f02b80e

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot}. This method assumes that the % TODO: Dette må forbedres
estimated effects are normally distributed with means equal to the
effects. The means of all estimated effects are zero. Resulting in a
plot where the estimated effect would end up on a straight line. This
plot is then testing whether all the estimated effects have the same
distribution. All deviations of the straight line indicates a
significant factor. In our results we have used the absolute value of
the effects, also called a half-normal plot. The advantages of using
the half-normal plot is that all large estimated effects will end up
in the top right corner. This means that the highest performance
significance will end up in the top right corner. The
axes themselves are not important to understand the plot nor the
results, refer to \cite{PlanExp} for details.
We have also set  the significance level at $\alpha =
0.05$, where \textsf{DanielPlot} is using Lenth's method for the
analysis of unreplicated factorials.

>>>>

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot} to create half-normal plots. The
intuition behind this is simple: If errors are normally distributed,
which is a conservative assumption, and there are no significant
effects they will also be normally distributed, and so the estimated
effects would end up on a straight line. Any significant deviations
from a straight line indicates a significant factor. That we use a
half-normal plot (rather than a normal plot) means that
the most significant effects will end up in the top right
corner. The axes themselves are not important to understand the plot
nor the results, refer to \cite{PlanExp} for details.  We have also
set the significance level at $\alpha = 0.05$, where
\textsf{DanielPlot} is using Lenth's method for the analysis of
unreplicated factorials.
